Dark matter halo shape at $z=0$ in the Auriga simulations: radial evolution and alignment with the stellar disk

### 2019-07-19 Document/paper.tex
edit

Our second results deals with the shape alignment as a function of
radius. 
In concordance with previous results in DM only simulations we find
that the shells of halo shape are well aligned at different radii.
However, in the presences of baryons these shells twist as a function
of radius.
\citep{Debattista08} found a similar effect, but only at radii smaller
than the disk radius. At radii larger than the disk radius, they find,
the dark matter shells stop twisting.
In our case the he twisting effect is robust across our sample of 30
halos at all radii,
its strenght also correlates with the halo triaxiality for radii
smaller than $0.12R_{200}$. 
At larger radii 
Also surprisingly at a radius of $0.25R_{200}\approx 56$ kpc the
alignment between the stellar disk and the dark matter halo is almost
perfect.

>>>>

Our second results deals with the disk-halo shape alignment as a function of
radius. 
In concordance with previous results in DM only simulations we find
that the shells of halo shape are well aligned at different radii.
However, in the presences of baryons these shells twist as a function
of radius.
At a radius of $0.25R_{200}\approx 56$ kpc the alignment between the
stellar disk and the dark matter halo is almost perfect and degrades
at other radii. 
This twisting effect, the change of disk-halo alignment as
a function of radius, is robust across our sample of 30
halos at all radii, its strenght correlating strongly with halo
triaxiality measured at $0.12R_{200}$.

This makes that 
\citep{Debattista08} found a similar effect, but only at radii smaller
than the disk radius. At radii larger than the disk radius, they find,
the dark matter shells stop twisting.
